\LARGE Performance Evaluation of Xenomai 3

### 2015-10-21 paper.tex
Fix double label, add ref to table 1
revise the synatx

\begin{abstract}
Xenomai 3 is the new architecture of the real-time framework running seamlessly side-by-side Linux as a dual-kernel system like Xenomai 2, or natively over mainline Linux kernels supplemented by the PREEMPT\_RT efforts to meet stricter response time requirements than standard kernel preemption would bring. In this presentation, we will evaluate the performances of Xenomai 3 running with dual-kernel configuration and analyze the various benchmarks for ARM Cortex-A series. Xenomai 3 introduces some optimizations over RTOS API emulation, thread-to-thread communications, and significantly lower overhead with dual-kernel configurations. The comprehensive performance comparisons illustrate the major evolution of Xenomai 3 along with the revised Real-Time Driver Model (RTDM) which provides a unified interface over both PREEMPT\_RT and dual-kernel.

>>>>

\begin{abstract}
Xenomai 3 is the new architecture of the Linux real-time framework that runs seamlessly side-by-side Linux as a dual-kernel system like Xenomai 2, or natively over mainline Linux kernels. The mainline Linux kernels in the latter condition can be supplemented by the PREEMPT\_RT efforts to meet stricter response time requirements than standard kernel preemption would bring. In this presentation, we will evaluate the performances of Xenomai 3 running with dual-kernel configuration and analyze the various benchmarks for ARM Cortex-A series. Xenomai 3 introduces some optimizations over RTOS API emulation, thread-to-thread communications, and significantly lower overhead with dual-kernel configurations. The comprehensive performance comparisons illustrate the major evolution of Xenomai 3 along with the revised Real-Time Driver Model (RTDM) which provides a unified interface over both PREEMPT\_RT and dual-kernel.
